---
title: "p8105_hw6_sc4935"
author: "Shiwei Chen"
date: "12/3/2021"
output: github_document
---

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(broom)
library(modelr)
library(mgcv)
library(dbplyr)
```


# Problem 1

Load and clean the data for regression analysis
```{r}
# convert numeric to factor where appropriate
childbwt_tidy = read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>%
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  )

childbwt_tidy

# check for missing data
check_na = childbwt_tidy %>% 
  map(~sum(is.na(.)))

check_na

# Count missing data
sum(is.na(childbwt_tidy))
```


Propose a regression model for birthweight. 
```{r}
bwt_model = lm(bwt ~ fincome + frace + malform + momage + mrace + ppbmi + smoken, data = childbwt_tidy)

summary(bwt_model)
coef(bwt_model)

bwt_model %>% 
   broom::tidy() %>% 
   knitr::kable(digits = 3)
```

## Describe your modeling process

### The predictors I choose:
fincome: family monthly income 

frace: father’s race 

malform: presence of malformations that could affect weight 

momage: mother’s age at delivery 

mrace: mother’s race 

ppbmi: mother’s pre-pregnancy BMI

smoken: average number of cigarettes smoked per day during pregnancy

Firstly, the exposures of family income, the race of parents will help me to find out the social status of family of new born baby. Second, I choose the predictors of mother’s age at delivery, mother’s pre-pregnancy BMI, and whether smoken to find out the health state of mother. Finally, the presence of malformations that could affect weight can see if the exposure directly affect babyweight.

In brief, according to many research, the social status of family, mother's health state, and the presence of malformations might affect the babyweight directly or indirectly.


Show a plot of model residuals against fitted values
```{r}
modelr::add_predictions(childbwt_tidy, bwt_model)
modelr::add_residuals(childbwt_tidy, bwt_model)
```

```{r}
childbwt_tidy %>% 
  modelr::add_predictions(bwt_model) %>% 
  modelr::add_residuals(bwt_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = .5) + 
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  labs(
    x = "Predicted values",
    y = "Residuals",
    title = "Residuals against predicted values"
  )
```

So, we can see the residuals against predicted values is symmetric about X-axis(y = 0). And the residual plot has a mostly CONSTANT pattern across the X-axis.

Compare your model to two others
```{r}
# One using length at birth and gestational age as predictors(main effects only)
model1 = lm(bwt ~ blength + gaweeks, data = childbwt_tidy) %>% 
  broom::tidy() 
  
# One using head circumference, length, sex, and all interactions(including the three-way interaction) between these
model2 = lm(bwt ~ babysex * blength * bhead, data = childbwt_tidy) %>% 
  broom::tidy() 
```


Make this comparison in terms of the cross-validated prediction error
```{r}
cv_df = 
  crossv_mc(childbwt_tidy, 100)

cv_df %>% pull(train) %>% .[[1]] %>% as_tibble

cv_df %>% pull(test) %>% .[[1]] %>% as_tibble

cv_df =
  cv_df %>%
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    bwt_model = map(train, ~lm(bwt ~ fincome + frace + malform + momage + mrace + ppbmi + smoken, data = .x)),
    model1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model2 = map(train, ~lm(bwt ~ babysex * blength * bhead, data = .x))
    ) %>% 
  mutate(
    rmse_bwt_model = map2_dbl(bwt_model, test, ~rmse(model = .x, data = .y)),
    rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
    rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y))
    )
```



```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
  labs(
    x = "Model",
    y = "RMSE",
    title = "Compare 3 models with rmse"
  )
```

So, from the violin plot, model 2(three-way interaction: head circumference, length, sex) seems have the loweset rmse, and the model I interested has the highest rmse.



# Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Use 5000 bootstrap samples, for each bootstrap sample, produce estimates of these two quantities
```{r}
boot_straps = 
  weather_df %>% 
  janitor::clean_names() %>%
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results)
```

```{r}
 boot_straps %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate)) %>% 
  knitr::kable(digits = 3)
```

Log function
```{r}
boot_straps_log = 
  boot_straps %>% 
  select(.id, term, estimate) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
    ) %>% 
  rename(intercept = "(Intercept)") %>% 
  mutate(log_beta = log(intercept*tmin))

boot_straps_log

  
boot_straps_log %>%   
  summarise(
    lower_quantile = quantile(log_beta, c(.025)), 
    upper_quantile = quantile(log_beta, c(.975))
    ) %>% 
  knitr::kable(digits = 3) 
  

boot_straps_log %>%  
  ggplot(aes(x = log_beta)) + 
  geom_density() +
  labs(
    x = "Log estimate",
    y = "Density",
    title = "Distribution of Log estimates"
  )
```

R Squared function
```{r}
boot_straps_r = 
  weather_df %>% 
  janitor::clean_names() %>%
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results)

boot_straps_r
  
boot_straps_r %>% 
    summarise(
    lower_quantile = quantile(r.squared, c(.025)), 
    upper_quantile = quantile(r.squared, c(.975))
    ) %>% 
  knitr::kable(digits = 3) 
  


boot_straps_r %>% 
  ggplot(aes(x = r.squared)) + 
  geom_density() +
  labs(
    x = "R.squared estimate",
    y = "Density",
    title = "Distribution of R.squared estimates"
  )
```

So, both plots of distribution(Log and R squared) are seems normal.
